Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-30 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-30 14-25-13

\section{Evaluation}\label{sec:evaluation}
\subsection{Algorithm time complexity}
In proposed algorithm, first, $Loss-rate(p,k^{'},k)$ is evaluated for all PV panel $p$ and target current level $Q_{k^{'}}$ with other current level $Q_{k}$.
This step takes $O(sn)$ where is $n$ is the number of panels and $s$ is the number of PV strings.
Then the algorithm iterate as follows:
\begin{enumerate}
\item\label{item:1} Sort panels by $Loss-rate$ and $M_{P}(Q_{k^{'}})$
\item\label{item:2} Select initial panels
\item\label{item:3} Remove redundant panels
\end{enumerate}

\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.

>>>>

\section{Evaluation}\label{sec:evaluation}
\subsection{Algorithm time complexity}\label{sec:algor-time-compl}
In proposed algorithm, first, $Loss-rate(p,k^{'},k)$ is evaluated for all PV panel $p$ and target current level $Q_{k^{'}}$ with other current level $Q_{k}$.
This step takes $O(sn)$ where is $n$ is the number of panels and $s$ is the number of PV strings.
Then the algorithm iterate as follows:
\begin{enumerate}
\item\label{item:1} Sort panels by $Loss-rate$ and $M_{P}(Q_{k^{'}})$
\item\label{item:2} Select initial panels
\item\label{item:3} Remove redundant panels
\end{enumerate}

When selecting panels for target current level PV string, to sort panels, we use a lexicographically order of $Loss-rate$ and $M_{P}(Q_{k_{'}})$.
It can be done by sort panels recursively from the first component, that is, we sort panels by $Loss-rate(p,k^{'},k)$, then, sort panels with same level by $Loss-rate(p,k^{'},k+1)$ and so on.
Since values of $Loss-rate$ and $M_{P}(Q_{k^{'}})$ are related to the number of modules of PV panel and typically there are three PV modules in a commercial PV panel.
Thus,we can use a bucket sort with 4 buckets.
Therefore, it takes $O(n)$ for each bucket sort and $O(sn)$ for a lexicographical sorting in total.
For initial selection, we check the panels in the sorted order, and we check panels again in reverse order to find and remove redundant panels.
Therefore, these two steps take $Q(n)$.
Since it takes $O(sn)$ for each PV string in addition to $O(sn)$ to obtain ``$loss$'' levels, the proposed algorithm takes $Q(s^{2}n)$ in total.
% $\dots$,$Loss-rate(p,k^{'},s)$, M$_{p}(Q_{k^{'}})$.
\subsection{Experimental setup}\label{sec:experimental-setup}
To evaluate proposed methods, we prepared MPP information of 100 mismatched PV arrays and applied algorithms.
Exhaustive searching algorithm is also applied for comparison.
MPP information is setup as follows for each PV array.
Each PV array has 4 - 20 PV panels and the number of panels is randomly determined.
Three current values are randomly assigned to the three PV modules in each panel from 2 - 20 current values, where the number of possible current values are also randomly determined for each PV array.
The number of strings is 2 - 8 and it is randomly determined for each PV array.

We first applied the method in~\cite{Orozco-Gutierrez2016} to select configuration candidates.
% as shown in step 1 and step 2.
Condition \textbf{Feasibility 1} is applied to exclude a part of infeasible configurations, and then configurations that generate more than 77\% of maximum power are selected from the remaining candidates as mentioned in~\cite{Orozco-Gutierrez2016}.
In the experiments, 384 candidates are selected from 100 PV arrays as shown in Table.
That is, for each PV array, 3 - 4 candidates are selected in average.
\subsection{Experimental results}\label{sec:experimental-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.
